---
title: "Assignment 2 - Jthacke1"
author: "Julia Thacker"
date: "10/1/2021"
output: html_document
---
Made LP model with 0 constraints and 9 decision variables
```{r}
library(lpSolveAPI)
lprec <- make.lp(0,9)
set.objfn(lprec, c(420, 420, 420, 360, 360, 360, 300, 300, 300))
```
Set the objective function: 420(L1+L2+L3) + 360(M1+M2+M3) + 300(S1+S2+S3)
With decision variables:
L1 = Large made in plant 1
L2 = Large made in plant 2
L3 = Large made in plant 3
M1 = Medium made in plant 1
M2 = Medium made in plant 2
M3 = Medium made in plant 3
S1 = Small made in plant 1         
S2 = Small made in plant 2  
S3 = Small made in plant 3
```{r}
lp.control(lprec,sense='max')
```
Set to maximum
```{r}
add.constraint(lprec, c(20,0,0,15,0,0,12,0,0),"<=",13000)
add.constraint(lprec, c(0,20,0,0,15,0,0,12,0),"<=",12000)
add.constraint(lprec, c(0,0,20,0,0,15,0,0,12),"<=",5000)
```
Added the three constraints for the square footage of the plants.
```{r}
add.constraint(lprec, c(1,0,0,1,0,0,1,0,0),"<=",750)
add.constraint(lprec, c(0,1,0,0,1,0,0,1,0),"<=",900)
add.constraint(lprec, c(0,0,1,0,0,1,0,0,1),"<=",450)
```
Three constraints for the number of units per day each plant has the excess capacity to produce.
```{r}
add.constraint(lprec, c(1,1,1,0,0,0,0,0,0),"<=",900)
add.constraint(lprec, c(0,0,0,1,1,1,0,0,0),"<=",1200)
add.constraint(lprec, c(0,0,0,0,0,0,1,1,1),"<=",750)
```
Three constraints for the number of units that would be sold per day in each size.
```{r}
add.constraint(lprec,(c(0,0,1,0,0,1,0,0,1)/(450))-(c(0,1,0,0,1,0,0,1,0)/(900)),"=",0)
add.constraint(lprec,(c(0,0,1,0,0,1,0,0,1)/(450))-(c(1,0,0,1,0,0,1,0,0)/(750)),"=",0)
add.constraint(lprec,(c(0,1,0,0,1,0,0,1,0)/(900))-(c(1,0,0,1,0,0,1,0,0)/(750)),"=",0)
```
Constraints for the plants to each use the same percentage of their excess capacity.
```{r}
lp.rownames <- c("1","2","3","4","5","6","7","8","9","10","11","12")
lp.colnames <- c("L1","L2","L3","M1","M2","M3","S1","S2","S3")
```
Named variables and constraints.
```{r}
solve(lprec)
get.objective(lprec)
get.variables(lprec)
```
Solved the model and pulled the objective and variables.
