---
title: "Module 11 Assignment - Quantitative Management Modeling"
author: "Julia Thacker"
date: "11/19/2021"
output:
  word_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(lpSolveAPI)
library(lpSolve)
ap.lp<-make.lp(0,7)
set.objfn(ap.lp,c(775,800,800,800,800,775,750))
lp.control(ap.lp,sense='min')
```
Created an LP model with 7 decision variables that will minimize the total wage expenses.
```{r}
set.type(ap.lp,c(1,2,3,4,5,6,7),"integer")
```
Set the type of the decision variables to integer.
```{r}
add.constraint(ap.lp, c(1,1,1,1,1,0,0),">=",19)
add.constraint(ap.lp, c(0,1,1,1,1,1,0),">=",18)
add.constraint(ap.lp, c(0,0,1,1,1,1,1),">=",27)
add.constraint(ap.lp, c(1,0,0,1,1,1,1),">=",22)
add.constraint(ap.lp, c(1,1,0,0,1,1,1),">=",26)
add.constraint(ap.lp, c(1,1,1,0,0,1,1),">=",25)
add.constraint(ap.lp, c(1,1,1,1,0,0,1),">=",21)
```
Added 7 constraints to account for the minimum number of workers required on each day of the week.
```{r}
print(ap.lp)
```

```{r}
solve(ap.lp)
get.objective(ap.lp)
```
Solved the model. The total cost of the optimal solution is $25,675.
```{r}
get.variables(ap.lp)
```
The optimal solution suggests 5 workers for shift 1, 1 for shift 2, 5 for shift 3, 0 for shift 4, 8 for shift 5, 4 for shift 6, and 10 for shift 7.

This result means that there would be 18 workers on Sunday, 27 on Monday, 27 on Tuesday, 28 on Wednesday, 25 on Thursday, 21 on Friday, and 19 on Saturday.







