---
title: "Module 8 Assignment - Quantitative Management Modeling"
author: "Julia Thacker"
date: "10/30/2021"
output:
  word_document: default
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(lpSolveAPI)
library(Benchmarking)
```

```{r}
x<-matrix(c(150,400,320,520,350,320,0.2,0.7,1.2,2,1.2,0.7),ncol = 2)
colnames(x)<-c("StaffHours","Supplies")
```

```{r}
y<-matrix(c(14000,14000,42000,28000,19000,14000,3500,21000,10500,42000,25000,15000),ncol = 2)
colnames(y)<-c("ReimbursedPatientDays","PrivatelyPaidPatientDays")
```
Created matrix x for the two inputs and martix y for the two outputs. Then performed DEA analysis under the assumptions of CRS, FDH, VRS, IRS, DRS and FRH. Also determined the Peers and Lambdas for each.
```{r}
e<-dea(x,y,RTS="CRS")
e
peers(e)
lambda(e)
dea.plot(x,y,RTS="CRS",ORIENTATION = "in-out",txt=LETTERS[1:6])
```

The CRS plot shows only facility 3 as efficient and the other 5 facilities are inefficient. This is the only formulation that resulted in only one facility being efficient. The CRS method would likely not be chosen by a firm because it produces results with the lowest performance.
```{r}
v<-dea(x,y,RTS="VRS")
v
peers(v)
lambda(v)
dea.plot(x,y,RTS="VRS",ORIENTATION = "in-out",txt=LETTERS[1:6])
```

The VRS plot shows that facilities 1, 3, and 4 are efficient and 2, 5, and 6 are not.
```{r}
i<-dea(x,y,RTS="IRS")
i
peers(i)
lambda(i)
dea.plot(x,y,RTS="IRS",ORIENTATION = "in-out",txt=LETTERS[1:6])
```
The IRS plot shows that only facilities 1 and 3 are efficient.
```{r}
d<-dea(x,y,RTS="DRS")
d
peers(d)
lambda(d)
dea.plot(x,y,RTS="DRS",ORIENTATION = "in-out",txt=LETTERS[1:6])
```
The DRS plot shows that facilities 3, and 4 are efficient and 1, 2, 5, and 6 are not efficient.
```{r}
f<-dea(x,y,RTS="FDH")
f
peers(f)
lambda(f)
dea.plot(x,y,RTS="FDH",ORIENTATION = "in-out",txt=LETTERS[1:6])
```
The FDH plot shows that facilities 1, 3, 4, and 6 are efficient while facilities 2 and 5 are not. This formulation resulted in the highest number of efficient facilities.

```{r}
g<-dea(x,y,RTS="add")
g
peers(g)
lambda(g)
dea.plot(x,y,RTS="add",ORIENTATION = "in-out",txt=LETTERS[1:6])
```
The add/FRH plot is similar to the FDH output, except now facility 6 is also shown as not efficient, along with facilities 2 and 5.


Facility 3 is the only facility that was shown as efficient under each of the assumptions. This means that facility 3 is the most efficient among the six facilities. Facilities 2 and 5 were not efficient under any of the assumptions.

